Abstraction and Invariance for Algebraically Indexed Types

### 2012-07-09 paper/section-introduction.tex
Lead in from units-of-measure; comment about omitted cases in isomorphism proof sketch

In this paper we show how to capture, and generalise, invariance under
groups of translations using
%Inspired by this connection, we study 
relational parametricity for types that are indexed by attributes with
algebraic structure. For example, in computational geometry, points in
2-space can be indexed by a coordinate frame; in physical modelling,
quantities are indexed by units-of-measure; in information-flow
security, computations are indexed by principals.  Types that are
polymorphic over such indices induce invariance properties and
abstraction barriers beyond those introduced by their unindexed
versions, as we now illustrate.

>>>>

In previous work the third author studied relational parametricity for
the types parameterized by units-of-measure, whose invariance 
properties relate to changes of units, or \emph{scaling}~\cite{kennedy97relational}. 
In this paper we investigate the general case of types indexed by attributes
with algebraic structure. For example, in computational geometry, points in
2-space can be indexed by a coordinate frame; in information-flow
security, computations are indexed by principals; in differential privacy, types
can be indexed by `distance'. Types that are
polymorphic over such indices induce invariance properties and
abstraction barriers beyond those introduced by their unindexed
versions, as we now illustrate.
